\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
Draft for conclusions/expected outcomes

Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.  With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.  These locks aren't invulnerable, but security professionals can certainly help bring them to the point where they can withstand basic attacks.

@@

\section{Expected Outcomes}
Not every penetration test finds a massive zero day vulnerability.  However, that doesn't mean a test isn't completely useless.  Tests may not often discover massive issues, but smaller issues are often prevalent.  Issues such as weaker cryptography, bad hardware intrusion detection, and magnetic locking overrides are common in locking hardware.

\section{Conclusions}
Words

>>>>

Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.  With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.  These locks aren't invulnerable, and security professionals can certainly help bring them to the point where they can withstand basic attacks.

@@

\section{Expected Outcomes}
Not every penetration test finds a massive zero day vulnerability.  However, that doesn't mean a test isn't completely useless.  Tests may not often discover massive issues, but smaller issues are often prevalent.  Issues such as weaker cryptography, issues with bad hardware intrusion detection, and bad endpoint security on older protocols are commonplace.  It should be expected to find several smaller issues rather than major flaws in the firmware or the device itself.

Overall, the authors expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.  Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.

\section{Conclusions}
Throughout this paper, the authors have discussed how to design a testing framework for attacking modern electronic locking technologies.  The authors listed out different types of attacks that could be run against a bluetooth-enabled locking solution.  Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.

We also discussed attacking the device from the backend, from the protocols that allow for the lock to communicate securely with an authentication server.  This includes the Wiegand protocol, which is not designed with a security focus in mind.

Lock picking may not yet be on the decline, but electronic locking mechanisms allow for greater viability for most organizations. Overall, electronic locking solutions will be used far into the future.  It's heavily important to test these locks to verify that the cryptographic and security mechanisms of these locks are structurally sound.
